---
title: " RStudio Tips & Tricks"
description: |
  a talk on RStudio IDE tips & tricks and other keyboard shortcuts
author:
  - first_name: "Samantha" 
    last_name: "Csik"
    url: https://samanthacsik.github.io/
    orcid_id: 0000-0002-5300-3075
    affiliation: Master of Environmental Data Science Program @ The Bren School (UCSB) & The National Center for Ecological Analysis and Synthesis
    affiliation_url: https://ucsb-meds.github.io/
date: 2021-11-15
slug: csik2021Rtipstricks
preview: lightbulb.gif
categories:
  - MEDS
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = FALSE}
xaringanExtra::embed_xaringan(
  url = "https://ucsb-meds.github.io/R-tips-and-tricks/#1",
  ratio = "4:3"
)
```

<br>

[`r fontawesome::fa("tv", fill = "#64605F", a11y = "sem")` slides](https://ucsb-meds.github.io/R-tips-and-tricks/#1) ~~ [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSB-MEDS/R-tips-and-tricks)

```{r icon-links, eval=TRUE, echo=FALSE}
# distilltools::icon_link(icon = "fas fa-tv",
#           text = "slides",
#           url = "https://ucsb-meds.github.io/cloud-computing/#1")
#           
#           
# distilltools::icon_link(icon = "fas fa-github",
#           text = "source code",
#           url = "https://github.com/UCSB-MEDS/cloud-computing")
```

# Overview

This talk was originally developed for the [Master of Environmental Data Science (MEDS) program](https://ucsb-meds.github.io/), administered by the [Bren School of Environmental Science & Management](https://bren.ucsb.edu/masters-programs/master-environmental-data-science) in partnership with the [National Center for Ecological Analysis and Synthesis](https://www.nceas.ucsb.edu/).

# Abstract

As environmental data scientists, we spend a lot of time in RStudio. Taking some time to learn how you can customize your RStudio IDE (**I**ntegrated **D**evelopment **E**nvironment) and the keyboard shortcuts used to navigate around that IDE can make you a more efficient (and happier) hacker!




