---
title: "Customizing Your Personal Website with CSS"
description: |
  a brief intro to using CSS to customize {distill} websites
author:
  - first_name: "Samantha" 
    last_name: "Csik"
    url: https://samanthacsik.github.io/
    orcid_id: 0000-0002-5300-3075
    affiliation: Master of Environmental Data Science Program @ The Bren School (UCSB) & The National Center for Ecological Analysis and Synthesis
    affiliation_url: https://ucsb-meds.github.io/
date: 2021-08-31
slug: csik2021css
preview: hacker.gif
categories:
  - MEDS
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = FALSE}
xaringanExtra::embed_xaringan(
  url = "https://ucsb-meds.github.io/customizing-websites-css/#1",
  ratio = "4:3"
)
```

<br>

[`r fontawesome::fa("tv", fill = "#64605F", a11y = "sem")` slides](https://ucsb-meds.github.io/customizing-websites-css/#1) ~~ [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSB-MEDS/customizing-websites-css)

```{r icon-links, eval=TRUE, echo=FALSE}
# distilltools::icon_link(icon = "fas fa-tv",
#           text = "slides",
#           url = "https://ucsb-meds.github.io/cloud-computing/#1")
#           
#           
# distilltools::icon_link(icon = "fas fa-github",
#           text = "source code",
#           url = "https://github.com/UCSB-MEDS/cloud-computing")
```

# Overview

This talk was originally developed for the [Master of Environmental Data Science (MEDS) program](https://ucsb-meds.github.io/), administered by the [Bren School of Environmental Science & Management](https://bren.ucsb.edu/masters-programs/master-environmental-data-science) in partnership with the [National Center for Ecological Analysis and Synthesis](https://www.nceas.ucsb.edu/).

# Abstract

Our MEDS students started off the inaugural year by learning how to create their own personal websites using the `{distill}` R package. This workshop offers an intro to CSS and how to use it to further customize `distill` sites. We cover how to change the default element styling (fonts, colors, sizes), how to create custom CSS rules, and how to find inspiration from other distill websites (and their source code) on the [distillery](https://distillery.rbind.io/).


